---
title: "KhelpeR: Descriptive Statistics"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Use_KhelpeR_descr_stats}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(KhelpeR)
library(data.table)
library(mlbench)
library(magrittr)
```

# Introduction 

KhelpeR is an R package that aims to provide useful functions for several tasks, e.g. exploratory data analysis or machine learning. 

# Exploratory Data Analysis 

```{r}
data("PimaIndiansDiabetes2")
dataset <- data.table::as.data.table(PimaIndiansDiabetes2)
```

## Continuous Statistics 

### Simple Continuous Statistics 

```{r}
KhelpeR::continuous_stats_overview(dataset) %>%
  KhelpeR::html_table()
```

### Extensive Continuous Statistics 

With the default parameter 'method = "all"' (=default), you get a table with extensive continuous statistics. 

```{r}
KhelpeR::continuous_stats(dataset) %>%
  KhelpeR::html_table()
```

Setting the parameter 'method' to "base", results in a table with basic continuous statistics. 

```{r}
KhelpeR::continuous_stats(dataset, method = "base") %>%
  KhelpeR::html_table()
```

Setting the parameter 'method' to "others", results in a table with the more complex other part of the continuous statistics. 

```{r}
KhelpeR::continuous_stats(dataset, method = "others") %>%
  KhelpeR::html_table()
```

### Grouping 

It is also possible to introduce a grouping variable to the function to show the statistics for each variable and group separately.

```{r}
KhelpeR::continuous_stats(dataset, group_var = "diabetes") %>%
  KhelpeR::html_table()
```

#### Extensive Continuous Statistics per Category

```{r}
KhelpeR::continuous_stats_grouped(dataset, variable = "glucose", group_var = "diabetes") %>%
  KhelpeR::html_table()
```

## Plotting

### Boxplots

```{r}
KhelpeR::plot_boxplot(dataset, variable = "glucose", title = "Glucose distribution", ylab = "Glucose")
```

```{r}
KhelpeR::plot_boxplot(dataset, variable = "glucose", group_var = "diabetes",
                      title = "Glucose distribution by presence of diabetes", ylab = "Glucose", xlab = "Diabetes")
```


## Table 1 

### Descriptive Numerical Data 

Every paper has a 'Table 1' to show descriptive statistics about the data set. The function 'fillTable1Num()' easily creates this table for numerical data. 

```{r}
KhelpeR::kable_table(KhelpeR::fillTable1Num(dataset))
```

You can also create 'Table 1' grouped by a grouping variable. This adds the calculation of the homoscedasticity between the respective groups for each variable. It is also possible to specify the number of digits in the output table. 

```{r}
KhelpeR::kable_table(KhelpeR::fillTable1Num(dataset, group_var = "gear", digits = 3))
```

## Descriptive Categorical Data 

```{r}
KhelpeR::kable_table(KhelpeR::fastCatStats(dataset))
```

```{r}
KhelpeR::kable_table(KhelpeR::fastCatStats(dataset, show_levels = TRUE))
```

# Group comparisons

```{r}
KhelpeR::binary_results(
  dataset = dataset,
  group_var = "diabetes"
) %>%
  KhelpeR::html_table(merge_rows = "binary_results")
```

