---
title: "Use_KhelpeR"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Use_KhelpeR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(KhelpeR)
library(data.table)
```

# Introduction 

KhelpeR is an R package that aims to provide useful functions for several tasks, e.g. exploratory data analysis or machine learning. 

# Exploratory Data Analysis 

```{r}
# import data
dataset <- data.table::data.table(datasets::mtcars)
dataset[,("gear"):=factor(get("gear"))]
```

## Numeric Statistics 

### Simple Numeric Statistics 

```{r}
KhelpeR::fastNumStats(dataset)
```

### Extensive Numeric Statistics 

With the default parameter 'method = "all"', you get a table with extensive numerical statistics. 

```{r}
KhelpeR::numStatsTable(dataset)
```

Setting the parameter 'method' to "base", results in a table with basic numerical statistics. 

```{r}
KhelpeR::numStatsTable(dataset, method = "base")
```

Setting the parameter 'method' to "others", results in a table with the complexer other part of the numeric statistics. 

```{r}
KhelpeR::numStatsTable(dataset, method = "others")
```

### Grouping 

It is also possible to introduce a grouping variable to the function to show the statistisics for each variable and group separately.

```{r}
KhelpeR::numStatsTable(dataset, group_var = "gear", method = "base")
```

## Table 1 

Every paper has a 'Table 1' to show descriptive statistics about the data set. The function 'fillTable1()' easily creates this table. 

```{r}
KhelpeR::fillTable1Num(dataset)
```

Even grouped by a grouping variable and more digits. 

```{r}
KhelpeR::fillTable1Num(dataset, group_var = "gear", digits = 3)
```
