---
title: "KhelpeR: Descriptive Statistics"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Use_KhelpeR_descr_stats}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(KhelpeR)
library(data.table)
library(mlbench)
library(magrittr)
```

# Introduction 

KhelpeR is an R package that aims to provide useful functions for several tasks, e.g. exploratory data analysis or machine learning. 

# Exploratory Data Analysis 

```{r}
data("PimaIndiansDiabetes2")
dataset <- data.table::as.data.table(PimaIndiansDiabetes2)
```

## Continuous Statistics 

### Simple Continuous Statistics 

```{r}
KhelpeR::continuous_stats_overview(dataset) %>%
  KhelpeR::html_table()
```

### Extensive Continuous Statistics 

With the default parameter 'method = "all"' (=default), you get a table with extensive continuous statistics. 

```{r}
KhelpeR::continuous_stats(dataset) %>%
  KhelpeR::html_table()
```

Setting the parameter 'method' to "base", results in a table with basic continuous statistics. 

```{r}
KhelpeR::continuous_stats(dataset, method = "base") %>%
  KhelpeR::html_table()
```

Setting the parameter 'method' to "others", results in a table with the more complex other part of the continuous statistics. 

```{r}
KhelpeR::continuous_stats(dataset, method = "others") %>%
  KhelpeR::html_table()
```

### Grouping 

It is also possible to introduce a grouping variable to the function to show the statistics for each variable and group separately.

```{r}
KhelpeR::continuous_stats(dataset, group_var = "diabetes") %>%
  KhelpeR::html_table(merge_rows = "continuous_stats")
```

#### Extensive Continuous Statistics per Category

```{r}
KhelpeR::continuous_stats_grouped(dataset, variable = "glucose", group_var = "diabetes") %>%
  KhelpeR::html_table()
```

## Plotting

### Boxplots

```{r}
KhelpeR::plot_boxplot(dataset, variable = "glucose", title = "Glucose distribution", ylab = "Glucose")
```

```{r}
KhelpeR::plot_boxplot(dataset, variable = "glucose", group_var = "diabetes",
                      title = "Glucose distribution by presence of diabetes", ylab = "Glucose", xlab = "Diabetes")
```

# Group comparisons

## Text based results

```{r}
KhelpeR::binary_results(
  dataset = dataset,
  group_var = "diabetes"
) %>%
  KhelpeR::html_table(merge_rows = "binary_results")
```


## Numeric results

```{r}
KhelpeR::binary_results(
  dataset = dataset,
  group_var = "diabetes",
  text_results = FALSE
) %>%
  KhelpeR::html_table(merge_rows = "binary_results_table")
```

## Get vector of variable names with significant test results

```{r}
KhelpeR::binary_significant_vars(
  dataset = dataset,
  group_var = "diabetes"
)
```

# Table 1

## Continuous variables

```{r}
KhelpeR::continuous_stats_table1(
  dataset = dataset
) %>%
  KhelpeR::html_table()
```

```{r}
KhelpeR::continuous_stats_table1(
  dataset = dataset,
  group_var = "diabetes"
) %>%
  KhelpeR::html_table(merge_rows = "continuous_stats_table1")
```

