---
title: "Use_KhelpeR: Descriptive Statistics"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Use_KhelpeR_descr_stats}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(KhelpeR)
library(data.table)
```

# Introduction 

KhelpeR is an R package that aims to provide useful functions for several tasks, e.g. exploratory data analysis or machine learning. 

# Exploratory Data Analysis 

```{r}
# import data
dataset <- data.table::data.table(datasets::mtcars)
vec <- c("cyl", "gear", "vs", "am", "carb")
dataset[,(vec):=lapply(.SD, factor), .SDcols=vec]
```

## Numeric Statistics 

### Simple Numeric Statistics 

```{r}
KhelpeR::kableTable(KhelpeR::fastNumStats(dataset))
```

### Extensive Numeric Statistics 

With the default parameter 'method = "all"' (=default), you get a table with extensive numerical statistics. 

```{r}
KhelpeR::kableTable(KhelpeR::numStatsTable(dataset))
```

Setting the parameter 'method' to "base", results in a table with basic numerical statistics. 

```{r}
KhelpeR::kableTable(KhelpeR::numStatsTable(dataset, method = "base"))
```

Setting the parameter 'method' to "others", results in a table with the complexer other part of the numeric statistics. 

```{r}
KhelpeR::kableTable(KhelpeR::numStatsTable(dataset, method = "others"))
```

### Grouping 

It is also possible to introduce a grouping variable to the function to show the statistisics for each variable and group separately.

```{r}
KhelpeR::kableTable(KhelpeR::numStatsTable(dataset, group_var = "gear", method = "base"))
```

#### Extensive Numeric Statistics per Category

```{r}
KhelpeR::kableTable(KhelpeR::numStatsTablePerCat(dataset, "mpg", "gear"))
```

## Table 1 

### Descriptive Numerical Data 

Every paper has a 'Table 1' to show descriptive statistics about the data set. The function 'fillTable1Num()' easily creates this table for numerical data. 

```{r}
KhelpeR::kableTable(KhelpeR::fillTable1Num(dataset))
```

You can also create 'Table 1' grouped by a grouping variable. This adds the calculation of the homoscedasticity between the respective groups for each variable. It is also possible to specify the number of digits in the output table. 

```{r}
KhelpeR::kableTable(KhelpeR::fillTable1Num(dataset, group_var = "gear", digits = 3))
```

## Descriptive Categorical Data 

```{r}
KhelpeR::kableTable(KhelpeR::fastCatStats(dataset))
```

```{r}
KhelpeR::kableTable(KhelpeR::fastCatStats(dataset, show_levels = TRUE))
```

